---
title: "Final Project"
description: |
  New dataset

date: "`r Sys.Date()`"
output: distill::distill_article

---
The dataset used for this project come from Kaggle, and it shows how fuel prices correlate with Unemployment. In this project, I will try to predict that the higher the unemployment leads to higher gas prices.

We begin by looking at the descriptive analytics.The standard deviation shows that Fuel Prices are close to the norm at 0.43, while Unemployment is skewed by 1.88.

The machine learning model used is the K-nn (Nearest Neighbor) model. This model is an algorithim that can solve classification and regression problems.

```{r}
load(file="Features_data_set.rda")
library(tidyverse)
library(caret)
Features_data_set=na.omit(Features_data_set)
```
```{r}
knitr::kable(psych::describe(Features_data_set))%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")
```


```{r}
ggplot(data=Features_data_set,mapping = aes(x=Fuel_Price,y=Unemployment,color=Store))+geom_point(alpha=0.5)

```

```{r}
#this creates an index of rows in include in the training
#literally lists the rows to keep
trainIndex <- createDataPartition(Features_data_set$Fuel_Price, p = .6, list = FALSE, times = 1)

#rows to keep
knitr::kable(trainIndex)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="200px")

#grab the data
#take these rows
FuelTrain <- Features_data_set[ trainIndex,]
#don't take these rows
FuelTest  <- Features_data_set[-trainIndex,]

#we now have training and testing data sets


```

```{r, echo=TRUE}
#for the algorithm we are using it requires that we standardize

#center= subtract the means and 
#scale = divide by standard deviation
#?preProcess sets the conversion up 
preProcValues <- preProcess(FuelTrain, method = c("center", "scale"))

preProcValues
```

```{r, echo=TRUE}
#this predict actual change the variables
trainTransformed <- predict(preProcValues, FuelTrain)
#repeat for testing
preProcValues <- preProcess(FuelTest, method = c("center", "scale"))
testTransformed <- predict(preProcValues, FuelTest)

```

```{r, echo=TRUE}
#data is split and standardized
#time to run the model
#fit knn

#use train function and set up the equation
knn_fit<-train(Fuel_Price~Unemployment,
              #data we are using
              data=trainTransformed,
              #algorithm we are using
              method="knn",
              #the hyper parameter or tuning parameter is the
              #number of neighbors...here we set it to 5
              tuneGrid=data.frame(k=5))

#this is the object that holds the model
knn_fit

#predict on the test set
knn_pred<-predict(knn_fit,testTransformed)


```
The Root Mean Square Error (RMSE) for this data is 0.7862285 which means that the data is close to the line of best fit. A high RMSE, such as the one produced, means that there is a high possibility that the data used will not be able to make a prediction with the dataset used. This data can be useful because it will let you know if the data you are using will be a close prediction or not.
