---
title: "Final Project"
description: |
  New dataset

date: "`r Sys.Date()`"
output: distill::distill_article

---
The dataset used for this project come from Kaggle, and it shows how fuel prices correlate with Unemployment. In this project, I will try to predict that the higher the unemployment leads to higher gas prices.

We begin by looking at the descriptive analytics.The standard deviation shows that Fuel Prices are close to the norm at 0.43, while Unemployment is skewed by 1.88.

The machine learning model used is the K-nn (Nearest Neighbor) model. This model is an algorithim that can solve classification and regression problems.

```{r}
load(file="Features_data_set.rda")
library(tidyverse)
library(caret)
Features_data_set=na.omit(Features_data_set)
```
```{r}
knitr::kable(psych::describe(Features_data_set))%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")
```


```{r}
ggplot(data=Features_data_set,mapping = aes(x=Fuel_Price,y=Unemployment,color=Store))+geom_point(alpha=0.5)

```

```{r}
#this creates an index of rows in include in the training
#literally lists the rows to keep
trainIndex <- createDataPartition(Features_data_set$Fuel_Price, p = .6, list = FALSE, times = 1)

#rows to keep
knitr::kable(trainIndex)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="200px")

#grab the data
#take these rows
FuelTrain <- Features_data_set[ trainIndex,]
#don't take these rows
FuelTest  <- Features_data_set[-trainIndex,]

#we now have training and testing data sets


```

```{r, echo=TRUE}
#for the algorithm we are using it requires that we standardize

#center= subtract the means and 
#scale = divide by standard deviation
#?preProcess sets the conversion up 
preProcValues <- preProcess(FuelTrain, method = c("center", "scale"))

preProcValues
```

```{r, echo=TRUE}
#this predict actual change the variables
trainTransformed <- predict(preProcValues, FuelTrain)
#repeat for testing
preProcValues <- preProcess(FuelTest, method = c("center", "scale"))
testTransformed <- predict(preProcValues, FuelTest)

```

```{r, echo=TRUE}
#data is split and standardized
#time to run the model
#fit knn

#use train function and set up the equation
knn_fit<-train(Fuel_Price~Unemployment,
              #data we are using
              data=trainTransformed,
              #algorithm we are using
              method="knn",
              #the hyper parameter or tuning parameter is the
              #number of neighbors...here we set it to 5
              tuneGrid=data.frame(k=5))

#this is the object that holds the model
knn_fit

#predict on the test set
knn_pred<-predict(knn_fit,testTransformed)

```
```{r}
#fit simple linear regression model
model_int <- lm(Unemployment ~ Unemployment , data = FuelTrain)

int_results<-predict(model_int,FuelTest)
###compute fit
summary(model_int)

knitr::kable(caret::RMSE(int_results,FuelTest$Fuel_Price),col.names = "RMSE Test")
knitr::kable(caret::RMSE(int_results,FuelTrain$Fuel_Price),col.names = "RMSE Train")

FuelTest$Sample<-"Testing"
FuelTrain$Sample<-"Training"

Combined_Fuel<-rbind(FuelTest,FuelTrain)
#create regression plot with customized style
ggplot(Combined_Fuel,aes(x=Fuel_Price, y=Unemployment,color=Sample)) +
  geom_point(alpha=.5) +
  theme_minimal() +
  labs(x='Fuel Price', y='Unemployment', title='Linear Regression Plot') +
  theme(plot.title = element_text(hjust=0.5, size=20, face='bold')) +
  geom_abline(aes(slope=model_int$coefficients[[1]],intercept=0),color="red")
```
The Linear Regression Model shows that the data is extremely scattered and clustered to form any true conclusion from the data. This Model and the one above both show outliers in the same areas. Also, the RMSE are nearly identical for the Training data and the testing data.  This tells me that this is a bad set of data to use for analysis.

```{r}
library(tidyverse)
#create residuals
testwithpred<-as.data.frame(cbind(int_results,FuelTest))
#create residuals
testwithpred<-testwithpred%>%
  rename(prediction=int_results)%>%
  mutate(error=Fuel_Price-prediction)

#create regression plot with customized style
ggplot(testwithpred,aes(x=Fuel_Price, y=error)) +
  geom_point(alpha=.5,color="deepskyblue") +
  theme_minimal() +
  labs(x='Fuel_Price', y='Error', title='Regression Error Plot') +
  theme(plot.title = element_text(hjust=0.25, size=20, face='bold')) +
  geom_hline(yintercept=0,color="red",linetype="dashed")
```
The Regression Error Plot shows that the data in this data set creates a bad model for linear regression.