---
title: "Machine Learning Model"
description: |
  Classification

date: "`r Sys.Date()`"
output: distill::distill_article
---
Classification modeling is simply looking at the data and being able to separate them into certain categories. This type of data modeling predicts how well the data set will fall into one of the categories.

**Change the p=.6 to p=.75 in the Data Pre-Processing section. How did the classification results change?**

```{r, echo=TRUE, message=FALSE}
library(tidyverse)
library(caret)
#change the p=.6 to p=.75
#what does createDataPartition do?
#run the following code: ?createDataPartition

#this creates an index of rows in include in the training
#literally lists the rows to keep
trainIndex <- createDataPartition(iris$Species, p = .75, list = FALSE, times = 1)

#rows to keep
knitr::kable(trainIndex)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="200px")

#grab the data
#take these rows
irisTrain <- iris[ trainIndex,]
#don't take these rows
irisTest  <- iris[-trainIndex,]

#we now have training and testing data sets


```

```{r, echo=TRUE}
#for the algorithm we are using it requires that we standardize

#center= subtract the means and 
#scale = divide by standard deviation
#?preProcess sets the conversion up 
preProcValues <- preProcess(irisTrain, method = c("center", "scale"))

preProcValues
```

```{r, echo=TRUE}
#this predict actual change the variables
trainTransformed <- predict(preProcValues, irisTrain)
#repeat for testing
preProcValues <- preProcess(irisTest, method = c("center", "scale"))
testTransformed <- predict(preProcValues, irisTest)

```

```{r, echo=TRUE}
#data is split and standardized
#time to run the model
#fit knn

#use train function and set up the equation
knn_fit<-train(Species~Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
              #data we are using
              data=trainTransformed,
              #algorithm we are using
              method="knn",
              #the hyperparameter or tuning parameter is the
              #number of neighbors...here we set it to 5
              tuneGrid=data.frame(k=5))

#this is the object that holds the model
knn_fit

#predict on the test set
knn_pred<-predict(knn_fit,testTransformed)

#confusion matrix gives us the results
confusionMatrix(knn_pred,testTransformed$Species)
```

Classification uses a training and testing data set in order to find patterns in future sets of data. An example is using a decision tree to determine how to proceed with the data set. This can be used in accounting when performing an audit.


